\section{Introduction}\label{sec:Introduction}
In the European-Union learn 94.5\% of the population english in school. In some areas like the Netherlands or the Czech Republic eveb 100\%\cite{europa}. It is due to this clear that english is used as an bridge-language to communicate between europeans from different countries.  \\
Through new technologies and the fall away of border is it easier then ever to communicate with people from different countries. And of course we use english more and more on a daily basis. In the german language are words like sexy, laptop, fast food, wellness and many more widely spread[CITE FEHLT]. Furthermore could advertising not live without english anymore (e.G. Douglas - Your partner in beauty). The german language goes even a step further and invents its own english words (e.G Handy is german for mobile-phone).   \\
It is therefore interesting to look at code-switching between english and other languages. In this paper we will look at tweets containing english and spanish words. Our goal is it to find out the language for each word. \\
In this paper we perform a language identification using machine learning techniques. Those techniques are able to indeficate the language of a single word without looking at the sentence. After the machine learning algorithm has indetificated the languages of each word, we try to improve the result using statistical facts of code-switching. We have with example observed that code-switching occurs very rarely in between two other words of the same language.\\VERGLEICH VERSCHIEDENER ANSÄTZE? LINEARE REGRESSION /  NEURONALE NETZE
\\
The data we are using are provided by \textit{First Workshop on Computational Approaches to Code Switching}\cite{workshop}. We have 11.400 Spanish-English tweets. Some of them are deleted or invalid thus we have XXX tweets and XXX different words. We know the language of each word in every tweet. \\
To evaluate our methods the workshop\cite{workshop} provided us with addional test- and trial-tweets.
SECTION X DOES LALALALA SECTION Y DOES LALALALA


%The tweets are from multiple different users. Thus the tweets are independent from each other. 